---
title: "Biblica Bible webscraping"
author: "Roger Soh"
date: "2021"
output:
  html_document: default
  pdf_document: default
editor_options: 
  chunk_output_type: console
---

## Scraping Biblica Bible

```{r warning=FALSE, message=FALSE}
library(tidyverse)
library(rvest)
library(stringr)
library(purrr)
library(knitr)
library(lubridate)
```

Biblica.com 

```{r}
bibletext_new_testament <- data.frame(matrix(ncol= 4, nrow =0))
colnames(bibletext) <- c("book","chapter", "verse", "text")

bibletext_new_testament <- read.csv("./data/bible/bibletext_new_testament.csv") %>%
  select(-1)
```


```{r webscraping}
url1 <- "https://www.bible.com/bible/111/REV.22.NIV"

url_max <- url1 %>%
  str_match("(?<=\\.)(\\d+)") %>%
  as.integer()

url1 <- url1 %>%
  str_replace("(.*\\.)\\d+(\\.NIV)", "\\1")

for (i in 1:url_max[1]) {
  url <- str_c(url1, i, ".NIV")
  
  biblica_webscrap <- read_html(url)
  
  book_chapter <- html_elements(biblica_webscrap, "h1") %>%
    html_text() #select text of element
  
  #verse_text <-  html_elements(biblica_webscrap, "span>:not(.f)")
  verse_text <- html_elements(biblica_webscrap, ".label, .content") %>%
    html_text() %>%
    str_replace_all("^(\\d+)(?!.*:)", "@\\1&") %>%
    str_replace_all("#","") %>%
    str_replace("(The Holy Bible).*", "") %>%
    str_replace("(Copyright).*", "") %>%
    str_replace("(Used by).*", "") %>%
    str_flatten(collapse = " ") %>%
    str_replace_all("(Lord )(Lord)", "Lord ") %>%
    str_replace_all("\\s+", " ") %>%
    str_split("@")
  
  
  book_verse <- data.frame(book_chapter, verse_text) %>%
    as_tibble()
  
  colnames(book_verse) <- c("book_chap", "verse_text")
  
  book_verse <- book_verse %>%
    filter(verse_text != "")
  
  tmp_bibletext <- book_verse %>%
    separate(book_chap, c("book", "chapter"), sep = "\\s(?=\\d)") %>%
    separate(verse_text, c("verse", "text"), "& ")
  
  
  bibletext_new_testament <- rbind(bibletext_new_testament, tmp_bibletext)
  
  Sys.sleep(5)
}
```





```{r remove na in text}

bibletext_new_testament <- bibletext_new_testament %>%
  filter(!is.na(text)) %>%
  filter(text !="")

```



```{r save csv}
write.csv(bibletext_new_testament, "./data/bible/bibletext_new_testament.csv")

```






{r scraping}
for(i in 1:4) {
  url <- str_c("https://www.biblica.com/bible/niv/jonah/", i, "/")
  
  biblica_webscrap <- read_html(url)
  
  book_chapter <- html_elements(biblica_webscrap, "h1") %>%
    html_text() %>% #select text of element
    str_replace("\\s[:punct:]\\sNew International Version \\(NIV\\)" , "")
  #  str_replace("(^\\d)\\s","\\1-" )

  
  verse_text <- html_elements(biblica_webscrap, ".content") %>%
    html_text() %>%
    str_replace("1(?=[a-zA-Z])", "@1& ") %>%
    str_replace(".*(?=@)", "") %>%
    str_replace_all("(\\d+)(?=[a-zA-Z])", "@\\1& ") %>%
    str_replace_all('(\\d+)“', ' @\\1& \"') %>%
    str_flatten(collapse = " ") %>%
    str_split("@")
  
  book_verse <- data.frame(book_chapter, verse_text) %>%
    as_tibble()
  
  colnames(book_verse) <- c("book_chap", "verse_text")
  
  book_verse <- book_verse %>%
    filter(verse_text != "")
  
  tmp_bibletext <- book_verse %>%
    separate(book_chap, c("book", "chapter"), sep = "\\s(?=\\d)") %>%
    separate(verse_text, c("verse", "text"), "& ")
  
  
  bibletext_new_testament <- rbind(bibletext_new_testament, tmp_bibletext)
  
  Sys.sleep(5)
}


{r NUMBER 33}
i = 33
url <- str_c("https://www.biblica.com/bible/niv/ezekiel/", i, "/")

biblica_webscrap <- read_html(url)

book_chapter <- html_nodes(biblica_webscrap, "h1") %>%
  html_text() %>% #select text of element
  str_replace("\\s[:punct:]\\sNew International Version \\(NIV\\)" , "")


#verse_text <- html_nodes(biblica_webscrap, ".pi1 , .p")
verse_text <- html_nodes(biblica_webscrap, ".pi1 , .verse-span") %>%
  html_text() %>%
  str_replace_all("(^\\d)(?=[a-zA-Z])", "@\\1& ") %>%
  str_replace_all("(^\\d\\d)(?=[a-zA-Z])", "@\\1& ") %>%
  str_replace_all('\\s(\\d+)(?=[a-zA-Z])', " @\\1& ") %>%
  str_replace_all('(\\d+)“', ' @\\1& \"') 


{r}
verse_text <- verse_text %>%
  str_flatten(collapse = " ") %>%
  str_split("@")

book_verse <- data.frame(book_chapter, verse_text) %>%
  as_tibble()

colnames(book_verse) <- c("book_chap", "verse_text")

book_verse <- book_verse %>%
  filter(verse_text != "")

tmp_bibletext <- book_verse %>%
  separate(book_chap, c("book", "chapter")) %>%
  separate(verse_text, c("verse", "text"), "& ")

bibletext <- rbind(bibletext, tmp_bibletext)



